Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-04-05 paper/paper.tex
Stage the reviewed state

\RequirePackage{amsmath}
\documentclass{llncs}

@@

\renewcommand{\C}{\texttt{C} \xspace}

@@

\begin{abstract}
Linear variation is a topological characteristic of a function of two variables.
The problem of linear variation computing can be reduced to the problem
of counting connected components in a binary image with eight-connected connectivity.
The new hybrid method for the problem is presented.
The method is essentially a modification of a two-scan algorithm for labeling
that groups the pixels into $2 \times 2$ cells.

@@

In image restoration it is often necessary to consider the following problem.
How to restore an original undistorted image $v$, if it is known an observed
image $u_0$ and the relation between $u_0$ and $v$:
\begin{equation}
  u_0=v+n,
  \label{eq:imageRelation}
\end{equation}
where $n$ is a noise?
A common way for solving the problems \eqref{eq:imageRelation} is to use the
variational functionals.
One of the most widely used approaches is total variation
regularization [1]. % TODO fix bibliography
Let $J(u)$ be the following functional:
\begin{equation}
  J(u) = \frac12 \norm{u - u_0}^2 + \lambda TV(u),
  \label{eq:jFunctional}
\end{equation}
where $\norm{\cdot}$ is the $L_2$ norm and all function we consider belong to the class
$BV(\Omega)$, i.\,e. the class of bounded variation on the set $\Omega$ functions.
%
The expression $\frac12 \norm{n-n_0}^2$ is called a fidelity term and
$\lambda TV(u)$ is called a regularization term and $\lambda$ is regularization
parameter.

@@

The norm and modulus of the gradient are metrical characteristic of a function of
two variables.
Continuous functions of two variables also have a set of topological
characteristics referred to as linear variations.
Kronrod [2] % TODO fix bibliography
introduced the notion of a regular component of the level set of a
continuous function of two variables.
The simplest topological characteristic in the linear variation theory is a number
of regular components for all level sets of a function.
Full information about linear variations of a function is contained in the
one-dimensional tree of a function of two variables.
In [3, 4, 5] % TODO fix bibliography
was discussed the necessity of the using a linear variation in the
image restoration theory.

@@

This problem is equivalent to the problem of counting the number of connected
components (CC) in a binary image with 8-connectivity.
This is usually done through CC labeling, and many approaches for that are
known\cite{sterzh}.

@@

So the benchmark tables show three levels of optimization applied to
DFS, SUF and SUF2:
``no'' meaning no condensation, ``view'' meaning lazy memory-less condensation
and ``yes'' meaning that a temporary condensed image was constructed in memory.
For the latter case, the construction time was included into the overall measured
time of run.

@@

some results

\newcommand{\inputtable}[2]{
  \begin{figure}
    \centering
    \includegraphics[height=0.45\textheight, keepaspectratio]{pics/#1x#2.eps}
    \caption{Average CPU time per run on noise images $#1 \times #2$ px}
    \label{fig:noise#1x#2}
  \end{figure}
  \begin{table}[p]
    \centering
    \input{tables/#1x#2}
    \caption{Average CPU time per run on noise images $#1 \times #2$ px}
    \label{tab:noise#1x#2}
  \end{table}
}

@@

\section{Summary and future work}

@@

@@

\bibitem {sterzh}
Стержанов, М.:
Методики выделения связных компонент в штриховых бинарных изображениях.
Труды конференции ГрафиКон’2010. НИУ ИТМО. Санкт-Петербург. с. 169-174. (2010)

@@

>>>>

\RequirePackage{amsmath}
\documentclass[hidelinks]{llncs}

@@

\renewcommand{\C}{\texttt{C} \xspace}
\newcommand{\CXX}{\texttt{C++} \xspace}

@@

\begin{abstract}
The linear variation is a topological characteristic of the function of two variables.
The problem of linear variation computing can be reduced to the problem of counting connected components in a binary image with eight-connected connectivity.
%The new hybrid method for the problem is presented.
%The method is essentially a modification of a two-scan algorithm for labeling
%that groups the pixels into $2 \times 2$ cells.
This is usually done through connected components labeling, and many approaches for that are known.
This paper presents an efficient way to convert the initial binary image with 8-connectivity into a condensed (non-binary) image with new connectivity that is 2 times smaller in each dimension than the initial image.
Most approaches for connected components labeling are still valid for the new image.
As time and memory consumptions of conventional approaches usually depend linearly on the number of pixels,
running them on the condensed image can be up to 4 times more efficient than running on the initial image.
The method is essentially a modification of some known raster algorithms for labeling that groups pixels into $2 \times 2$ cells.
A performance benchmark of the proposed  method applied to some approaches on noise images is provided.

@@

In image restoration it is often necessary to consider the following problem.
How to restore an original undistorted image $v$, if it is known an observed
image $u_0$ and the relation between $u_0$ and $v$:
\begin{equation}
  u_0=v+n,
  \label{eq:imageRelation}
\end{equation}
where $n$ is a noise?
A common way for solving the problems \eqref{eq:imageRelation} is to use the
variational functionals.
One of the most widely used approaches is total variation
regularization\cite{mak1}.
Let $J(u)$ be the following functional:
\begin{equation}
  J(u) = \frac12 \norm{u - u_0}^2 + \lambda TV(u),
  \label{eq:jFunctional}
\end{equation}
where $\norm{\cdot}$ is the $L_2$ norm and all function we consider belong to the class
$BV(\Omega)$, i.\,e. the class of bounded variation on the set $\Omega$ functions.
%
The expression $\frac12 \norm{n-n_0}^2$ is called a fidelity term and
$\lambda TV(u)$ is called a regularization term and $\lambda$ is regularization
parameter.

@@

The norm and modulus of the gradient are metrical characteristic of a function of
two variables.
Continuous functions of two variables also have a set of topological
characteristics referred to as linear variations.
Kronrod\cite{mak2}
introduced the notion of a regular component of the level set of a
continuous function of two variables.
The simplest topological characteristic in the linear variation theory is a number
of regular components for all level sets of a function.
Full information about linear variations of a function is contained in the
one-dimensional tree of a function of two variables.
In \cite{mak3,mak4,mak5}
was discussed the necessity of the using a linear variation in the
image restoration theory.

@@

This problem is equivalent to the problem of counting the number of connected
components (CC) in a binary image with 8-connectivity.
This is usually done through CC labeling, and many approaches for that are
known\cite{hechao}.

@@

So the benchmark charts show three levels of optimization applied to
DFS, SUF and SUF2:
just method name in legend refers to method applied to non-condensed image,
``+view'' means lazy memory-less condensation
and ``+2x2'' means that a temporary condensed image was constructed in memory.
For the latter case, the construction time was included into the overall measured
time of run.

\subsection{Measurement}

For measurement purposes all algorithms and optimizations were implemented by us in \CXX.

The program was compiled using \texttt{g++ 5.3.0-3} compiler with \texttt{-O3} optimization flag.
All tests were run on same machine running under Arch Linux with standard \texttt{linux 4.4.1-2} kernel,
utilising non-overclocked \texttt{Intel(R) Core(TM) i5-2430M CPU @ 2.40GHz} (L3 cache size 3072K) processor and non-overclocked 1333MHz 8GiB Kingston RAM.

The test images were generated in the following manner. At first, 
for given density $d$, the first $4dNM$ pixels of
the $2N \times 2M$ image were filled with object values, while rest filled with background values.
Then all the pixels were permuted using \texttt{std::shuffle} function from \CXX standard library,
which is an implementation of Fisher-Yates Shuffle algorithm\cite{fisher:yates}.

All methods were run on same tests, which was achieved by supplying same seed to the
\texttt{std::mt19937} Mersenne Twister\cite{mt19937} random number engine implementation from \CXX standard library before passing the engine to \texttt{std::shuffle}.

@@

Line charts with benchmarks of mentioned algorithms on different noise images are shown on
\Cref{fig:noise400x600,fig:noise800x1200,fig:noise1200x1800,fig:noise2000x3000,fig:noise4000x6000}.

The extremely bigger CPU time for SUF and DTSUF methods on
huge images could be explained by significant increase in the number of cache-misses
produced by Union-Find.
The charts prove effectiveness of the $2 \times 2$ condensation optimization.

\newcommand{\inputtable}[2]{
  \begin{figure}
    \centering
    \includegraphics[height=0.45\textheight, keepaspectratio]{pics/#1x#2.eps}
    \caption{Average CPU time per run on noise images $#1 \times #2$ px.}
    \label{fig:noise#1x#2}
  \end{figure}
 % \begin{table}[p]
 %   \centering
 %   \input{tables/#1x#2}
 %   \caption{Average CPU time per run on noise images $#1 \times #2$ px}
 %   \label{tab:noise#1x#2}
 % \end{table}
}

@@

% \section{Summary and future work}

@@

\bibitem {mak1}
Rudin, L., Osher, S., Fatemi, E.: Nonlinear total variation based noised removal algorithms. Phys. D. 60, 259-268 (1992)

\bibitem {mak2}
Kronrod, A.: On functions of two variables ," Uspehi Mat. Nauk 5, 1(35), 24-134(1950)

\bibitem {mak3}
Makovetskii, A., Kober, V.: Image restoration based on topological properties of functions of two variables.  Proc. SPIE Applications of Digital Image Processing XXXV, 8499, 84990A (2012)

\bibitem {mak4}
4.	Makovetskii, A., Kober, V.: Modified gradient descent method for image restoration. Proc. SPIE Applications of Digital Image Processing XXXVI, 8856, 885608-1 (2013)

\bibitem {mak5}
Chochia, P., Milukova, O.: Comparison of Two-Dimensional Variations in the Context of the Digital Image Complexity Assessment.  Journal of Communications Technology and Electronics, 2015, 60, no. 12,  pp. 1432-1440

@@

%\bibitem {sterzh}
%Стержанов, М.:
%Методики выделения связных компонент в штриховых бинарных изображениях.
%Труды конференции ГрафиКон’2010. НИУ ИТМО. Санкт-Петербург. с. 169-174. (2010)

@@

\bibitem {fisher:yates}
 Fisher, A., Yates, F.:
 Statistical tables for biological, agricultural and medical research (3rd ed.). 
 London: Oliver \& Boyd. pp. 26–27. OCLC 14222135 (1948)

\bibitem{mt19937}
Matsumoto, M., Nishimura, T.:
"Mersenne twister: a 623-dimensionally equidistributed uniform pseudo-random number generator".
ACM Transactions on Modeling and Computer Simulation 8 (1): 3–30. (1998)
